---
title: "Reproducible document"
author: "Sabina Wagner"
format: html
---
## Setup code chunk

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(
    here::here("data/post-meal-insulin.csv")
)
```

## About me

- Sabina Wagner
- National Institute of Public Health, SDU

I am a phd student, working within the area of **stigma** related to *diabetes* and *overweight*

## Simple code

```{r}
3 * 3
```

## Other markdown

I can also write superscript^1^ and subscript~2~

## Git testing

Here is something that I have added to this document, and that I want to commit to git.

I am now making a second change, that I have committed.

## Showing the data

```{r}
post_meal_data
```
```{r}
glimpse(post_meal_data)
```
## Plots

```{r}
ggplot(post_meal_data,aes(x=BMI)) + 
    geom_histogram()
```

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histogram
ggplot(post_meal_data, aes(x = BMI)) + 
    geom_histogram()
```

Here is the distribution (see @fig-bmi-histogram)

## Exercise: Discrete plots

```{r}
#| fig-cap: "Groups"
#| label: fig-group
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group above for a cool plot!
