---
title: "Reproducible document"
author: "Sabina Wagner"
format: html
---
## Setup code chunk

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(
  here::here("data/post-meal-insulin.csv")
)
```

## About me

- Sabina Wagner
- National Institute of Public Health, SDU

I am a phd student, working within the area of **stigma** related to *diabetes* and *overweight*

## Simple code

```{r}
3 * 3
```

## Other markdown

I can also write superscript^1^ and subscript~2~

## Git testing

Here is something that I have added to this document, and that I want to commit to git.

I am now making a second change, that I have committed.

## Showing the data

```{r}
post_meal_data
```
```{r}
glimpse(post_meal_data)
```
## Plots

```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histogram
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

Here is the distribution (see @fig-bmi-histogram)

## Exercise: Discrete plots

```{r}
#| fig-cap: "Groups"
#| label: fig-group
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group above for a cool plot!

## Plotting two discrete variables

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar()
```

```{r}
post_meal_data |>
  ggplot(aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Putting two plots side by side

```{r}
#| label: fig-bmi-group
#| fig-cap: "BMI and group, side by side"
#| fig-subcap:
#|  - "Distribution of BMI"
#|  - "Group size"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```
## Plotting two continuous variables

```{r}
#| label: fig-bmi-aucpg
#| fig-cap: "BMI by area under curve glucose"
ggplot(post_meal_data, aes(x= BMI, y=auc_pg)) +
    geom_smooth() + geom_point()
```
## Pushing changes to remote 

## Pulling changes from remote
